R Notebook

### 2024-05-31 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
fb

>>>>

## Overall Plot (unstd. vs. std. over 81 participants)
df_heart_rate <-
  main %>%
  mutate(time = time / 60) %>%
  filter(time_span == "overall") %>%
  dplyr::select("ID","time","heart_rate") %>%
  distinct() %>%
  group_by(ID) %>%
  mutate(type = "a. Heart Rate (in beats per minute)") %>%
  summarise(time = time,
            mean_hr_unstd = mean(heart_rate,
                                 na.rm = TRUE)
            )

df_heart_rate_std <-
  main %>%
  mutate(time = time / 60) %>%
  filter(time_span == "overall") %>%
  dplyr::select("ID","time","heart_rate_std") %>%
  distinct() %>%
  group_by(ID) %>%
  summarise(time = time,
            mean_hr_std = mean(heart_rate_std,
                               na.rm = TRUE)
            ) %>%
  transmute(ID,
            time,
            type = "b. Heart Rate (standardized)",
            heart_rate = mean_hr_std)

loess_plot_std_unstd <-
  bind_rows(df_heart_rate,
            df_heart_rate_std
          ) %>%
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth(se = T,
              size = 0.5,
              colour = "black",
              level = 0.99) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0.01,0)) +
  labs(x = "Time (in minutes)",
       y = "",
       ) +
  theme_apa() +
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y")
